\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-03-14 papers/itsc_2012/final.tex
Edits to abstract and intro

\commentd{sounds fine to me, only thing is that we haven't actually focused on
  dynamic re-planning or any kind of overseer yet, although theres nothing
  stopping us from trying that idea again}
\commentp{If it's not implemented, we shouldn't talk about it.}

\begin{abstract} 
Autonomous vehicles have seen great advancements in recent years, and
such vehicles are now ever closer to being commercially available.
The advent of driver-less cars provides opportunities for optimizing
traffic in ways not possible before. This paper introduces an open
source multi-agent traffic simulator called AORTA, which stands for
\textit{Approximately Orchestrated Road Traffic Automata}, and
demonstrates its usage for optimizing autonomous traffic at a
city-wide scale. AORTA creates scale simulations by generating maps
using publicly available road data from \textit{OpenStreetMap}
(OSM). Simulations of specific regions throughout the world can be set
up in the few minutes it takes to export data for the region of
interest from OSM. AORTA focuses on interactions between agents by
defining \textit{behaviors} for individual vehicles and
intersections. These behaviors allow agents to interact with each
other as well as with an external \textit{overseer} that is
responsible for optimizing traffic flow. Overseers can interact with
these agents to allow for dynamic route re-planning to reduce traffic
load, optimized intersection navigation, and improved car following.
\commentpk{rest devoted to application}
\end{abstract}

@@

The arrival of driver-less cars presents several challenges that need to be
addressed in the near term. Road infrastructure needs to be updated to better
support autonomous vehicles.\commentp{Is this necessarily the case?
  It may be useful, but is it a need?} A number of legal and safety concerns need to be
addressed in the context of driver-less cars. Human drivers need new
methodologies to interact with autonomous drivers on public roads. At the same
time, driver-less cars provide opportunities of solving traffic problems in
ways that were never before possible. For instance, autonomous cars can be
quickly diverted to make way for emergency vehicles responding to an accident.
Even day-to-day traffic issues such as congestion could potentially be greatly
reduced by effective management of traffic flow. This work addresses
some of these problems.\commentp{Be more specific in this paragraph.
  Which of these challenges are eing addressed elsewhere (cite), and
  which are addressed in this paper?}
\commentp{Overall, this paragraph is a bit scattered.  I suggest
  something more like the following (after the first sentence).
  Several of the challenges are already being addressed.  For example
  .....
  This paper focusses on the specific challenge(s) of....}

@@

% Diagram made with gliffy.com. architecture.gxml should enable editing.
\begin{figure}
  \centering \includegraphics[scale=0.3]{architecture.png}
  \caption{A summary of AORTA's components.}
  \label{fig:arch}
  \vspace{-20pt}
\end{figure}

@@

The authors would like to thank Dr. Michael Quinlan for his support during the
seminal stages of AORTA and all OpenStreetMap contributers for providing free
maps.

@@

% They're sorted by order of citation, not alphabetically. IEEEtran.bst confirms
% this is the correct "numerical citation style."
\bibliographystyle{IEEEtran}
\bibliography{root}

>>>>

\begin{abstract} 
Autonomous vehicles have seen great advancements in recent years, and
such vehicles are now ever closer to being commercially available.
The advent of driver-less cars provides opportunities for optimizing
traffic in ways not possible before. This paper introduces an open
source multi-agent traffic simulator called AORTA, which stands for
\textit{Approximately Orchestrated Road Traffic Automata}, and
demonstrates its usage for optimizing autonomous traffic at a
city-wide scale. AORTA creates scale simulations by generating maps
using publicly available road data from \textit{OpenStreetMap}
(OSM). Simulations of specific regions throughout the world can be set
up in the few minutes it takes to export data for the region of
interest from OSM. AORTA focuses on interactions between agents by
defining \textit{behaviors} for individual vehicles and
intersections. These behaviors allow agents to interact with each
other as well as local intersections in any manner required for a
simulation of interest.
\commentpk{rest devoted to application}
\end{abstract}

@@

The arrival of driver-less cars presents several challenges that need to be
addressed in the near term. Road infrastructure changes could provide important
improvements for autonomous vehicles. A number of legal and safety concerns need to be
addressed in the context of driver-less cars. Human drivers need new
methodologies to interact with autonomous drivers on public roads. At the same
time, driver-less cars provide opportunities for solving traffic problems in
ways that were never before possible. For instance, autonomous cars can be
quickly diverted to make way for emergency vehicles responding to an accident.
Even day-to-day traffic issues such as congestion could potentially be greatly
reduced by effective management of traffic flow. This work addresses
some of these problems.\commentp{Be more specific in this paragraph.
  Which of these challenges are eing addressed elsewhere (cite), and
  which are addressed in this paper?}
\commentp{Overall, this paragraph is a bit scattered.  I suggest
  something more like the following (after the first sentence).
  Several of the challenges are already being addressed.  For example
  .....
  This paper focusses on the specific challenge(s) of....}

@@

% Diagram made with gliffy.com. architecture.gxml should enable editing.
\begin{figure*}
  \centering \includegraphics[scale=0.3]{architecture.png}
  \caption{A summary of AORTA's components.}
  \label{fig:arch}
  \vspace{-20pt}
\end{figure*}

@@

Dr. Quinlan has certainly been helpful.

What credits do we need to give to OSM?
\commentp{Just citing it is good enough.}

@@

\commentd{Er, these don't look like they're alphabetically sorted. And why is
the Google Maps entry so stretched?}

\bibliographystyle{IEEEtran}
\bibliography{root}
